Causal Discovery on Precarity and Depression

### 2024-12-28 draft_v1/draft_v1.qmd
add_PC_presum_result

>>>>

```{r}
#| layout-nrow: 2
#| label: fig-pc_presum
#| fig-cap: "Resulting graphs of precarity sum score and individual depression symptoms using PC"
#| fig-subcap: 
#|   - "Using both GaussianCI and RCoT"
#|   - "Using only RCoT"
#| fig-align: center
#| out-width: 70%

knitr::include_graphics("img/pc_presum_GaussianCIRCoT.png")
knitr::include_graphics("img/pc_presum_onlyRCoT.png")
```

### 2024-12-28 draft_v1/draft_v1.tex
add_PC_presum_result

>>>>

\includegraphics[width=0.7\textwidth,height=\textheight]{img/pc_presum_GaussianCIRCoT.png}

\subcaption{\label{fig-pc_presum-1}Using both GaussianCI and RCoT}

\includegraphics[width=0.7\textwidth,height=\textheight]{img/pc_presum_onlyRCoT.png}

\subcaption{\label{fig-pc_presum-2}Using only RCoT}

\caption{\label{fig-pc_presum}Resulting graphs of precarity sum score
and individual depression symptoms using PC}
